\textcolor[rgb]{0,0,1}{Data-Driven Model Predictive Control for Energy and Thermal Comfort Optimization in Building Energy Systems using Random Forests}

### 2018-01-20 paper/final/main.tex
Introduction and noisy forecast
git merge
Appendix Reg Trees

\usepackage{achinDefs}
\usepackage{lineno,hyperref}
\usepackage{slashbox}
\modulolinenumbers[5]
\usepackage{gensymb}
\usepackage{multirow}
\usepackage{eurosym}

@@

\title{Data Predictive Control with Random Forests:\\Theory and Applications}

@@

\appendix
\section{REGRESSION TREES}\label{AppendixRT}
TO BE DONE $\rightarrow$ \textcolor[rgb]{0,0,1}{Achin and Francesco}
\section{RANDOM FORESTS}\label{AppendixRF}
TO BE DONE $\rightarrow$ \textcolor[rgb]{0,0,1}{Achin and Francesco}
\end{document}

>>>>

\usepackage{achinDefs}
\usepackage{lineno,hyperref}
\usepackage{slashbox}
\modulolinenumbers[5]
\usepackage{gensymb}
\usepackage{multirow}
\usepackage{eurosym}
\usepackage{longtable}

\newtheorem{problem}{Problem}
\newtheorem{remark}{Remark}

@@

\title{\textcolor[rgb]{0,0,1}{Data-Driven Model Predictive Control for Energy and Thermal Comfort Optimization in Building Energy Systems using Random Forests}}

@@

\appendix
\input{appendixRegTrees.tex}
\end{document}
